Making Sequential Programs Deterministic

### 2019-03-31 experiments.tex
Tweak in NonDex experiments

\subsection{NONDEX case study}
\cite{nondex} reported flaky tests on 21 open source projects. The authors also reported the sources of flakiness
after manually inspecting these tests. We ran \TheDeterminismChecker on all these benchmarks with the objective
of measuring recall of our tool. We cloned all 21 repos and switched to the commit that had a flakiness issue as reported 
in~\cite{nondex}. Of these projects, \<handlebars> has a compile time failure which prevents us from running \TheDeterminismChecker on it. For benchmarks \<visualee>, \<easy-batch>, and \<vraptor>, we couldn't find
the sources of flakiness as reported in~\cite{nondex} anywhere in the respective repositories.
\TheDeterminismChecker reported the nondeterministic source locations correctly in the rest of the projects.
All these benchmarks and instructions to reproduce our results can be found at \href{https://github.com/t-rasmud/determinismCaseStudies}{https://github.com/t-rasmud/determinismCaseStudies}.
\todo{P4, P12 and P21 det checker isn't recognized?}

>>>>

\subsection{\OurTool on NonDex benchmarks}\label{sec:nondex-benchmarks}

\Cref{sec:nondex-randoop} shows that \ourTool finds errors that NonDex does not.
This section determines whether NonDex finds errors that \ourTool does not.
Its authors ran NonDex on 195 open-source projects, and NonDex found flaky tests in
21 of them.

The authors also reported the sources of flakiness
after manually inspecting these tests. We ran \TheDeterminismChecker on all these benchmarks with the objective
of measuring recall of our tool. We cloned all 21 repos and switched to the commit that had a flakiness issue as reported 
in~\cite{nondex}. Of these projects, \<handlebars> has a compile time failure which prevents us from running \TheDeterminismChecker on it. For benchmarks \<visualee>, \<easy-batch>, and \<vraptor>, we couldn't find
the sources of flakiness as reported in~\cite{nondex} anywhere in the respective repositories.
\TheDeterminismChecker reported the nondeterministic source locations correctly in the rest of the projects.
All these benchmarks and instructions to reproduce our results can be found at \href{https://github.com/t-rasmud/determinismCaseStudies}{https://github.com/t-rasmud/determinismCaseStudies}.
\todo{P4, P12 and P21 det checker isn't recognized?}
